---
title: "OPTICS_analysis"
output: word_document
---

```{r setup, include=F, message=F, warning=F}
knitr::opts_chunk$set(echo=F, warning=F, message=F)

set.seed(42)

#Declare vector of required packages
packages <- c("tidyverse", "readr", "dbscan")

#load function to check whether required packages are installed.
source("./functions/check_required_packages.R")
check_required_packages(packages)

#load required packages
lapply(packages, require, character.only=T)

#load data
data <- haven::read_spss("./data/dataE_clear5 2209.sav") %>% select(CASE, sexdrive2, CSBD, PPCS_6, meffort, socialanx, lon, mvalue, attr)

colnames(data) <- c("uid", "sex_drive", "csbd", "ppcs", "soi_r_me", "social_anxiety", "lon", "mvs", "attraction_to_children")

#load the results from the optics clustering
#optics_models <- readRDS(".GitHub/LPA_analysis/out/optics_models.RDS")
```

```{r optics, eval=F}
min_Pts = seq(5,20,by=5)
optics_models <- list()

folds <- lpa_models %>% select(nclust, fold, rep, folds,test_fold_uids) %>% filter(nclust==3)

for (p in min_Pts){
  optics_models[[as.character(p)]] <- lapply(folds %>% pull(folds), function(x) {dbscan::optics(x = data[x %>% unlist(),] %>% select(-uid), eps=NULL,minPts = p)}) 
}

optics_models <- tibble(names = optics_models %>% list_flatten() %>% names(), models = optics_models %>% list_flatten())

names <- optics_models %>% pull(names) %>% str_split_fixed("_", 2) %>% as_tibble() %>% rename(minPts=V1, fold=V2) 

names <- names %>% select(-fold) %>% cbind( names %>% pull(fold) %>% str_split_fixed("\\.", 2) %>% as_tibble() %>% rename(fold = V1, rep = V2))

optics_models <- cbind(names, optics_models)
optics_models <- optics_models %>% select(-names)

#We add the folds to the tibble so we have everything nice and tidy and in one place. 
train_folds <- replicate(4, folds %>% pull(folds), simplify = FALSE) %>% list_flatten()
test_folds <- replicate(4, folds %>% pull(test_fold_uids), simplify = FALSE) %>% list_flatten()

optics_models <-  optics_models %>%  mutate(folds = train_folds, test_fold_uids = test_folds)

optics_models <- optics_models %>% as_tibble()
```

```{r clustering, eval=F}
#It's very hard to find any recommendations on the value of xi. It tells the clustering algorithm what change in density a beginning and the end of a cluster marks. Therefore we refer to the values that are referenced in the OPTICS paper and expand the grid a bit. Given how computationally expensive DBCV is, we try just a few values around the default of scikitlearn. 
xi <- c(0.001, 0.05, 0.1)

#It appears furthermore that to make predictions in the end, we need to do a DBSCAN clustering. To guarantee that we will be able to predict new cluster memberships we also compute DBSCAN clustering epsilon_clust = epsilon.

for (p in xi){
  optics_models <- cbind(optics_models, lapply(1:nrow(optics_models), function(x){extractXi(optics_models$models[[x]], p)$cluster}) %>% as_tibble_col())
  colnames(optics_models)[ncol(optics_models)] <- paste(p, "Xi", sep="_")
}

#Now we want to extract the clustering for DBSCAN with a matching epsilon value determined by knndist and the kneedle algorithm. Sensitivity parameter was chosen by trying out a few values and looking at sample knndistgraphs.

optics_models <- optics_models %>% mutate(epsilon_clust = lapply(1:nrow(optics_models),function(i){
  dist <- kNNdist(x=data[optics_models$folds[[i]],] %>% select(-uid) %>% as.matrix(), k=optics_models$models[[i]]$minPts-1) %>% sort()

return(kneedle::kneedle(x=1:length(dist), y=dist, concave=TRUE, decreasing = FALSE, sensitivity = 15)[2])
}) %>% unlist())


optics_models <- optics_models %>% mutate(DBSCAN_clustering = lapply(1:nrow(optics_models), function(i){
  optics_models$models[[i]] %>% extractDBSCAN(eps_cl = optics_models$epsilon_clust[i])
  }))

optics_models <- optics_models %>% mutate(cv_predicted_clusters = lapply(1:nrow(optics_models), function(i){
  
predict(newdata=data[data$uid %in% (optics_models[i,] %>% pull(test_fold_uids) %>%unlist()),] %>% select(-uid),
        object =optics_models$DBSCAN_clustering[[i]],
        data = data[optics_models$folds[[i]],] %>% select(-uid))}))
```

We can inspect the predicted clustering now. As we can see, the overwhelming majority of models only identifies membership to one cluster in the new data, which makes sense. The models with more than one cluster are with the smaller minpts parameter, which makes the solution more fuzzy - since fewer points have to be found in the neighborhood of a point to make it a core point in the clustering algorithm. Usually values much larger than 5 are recommended. Further inspection of cluster indices is probably not worthwhile because they are not designed for the case of only one cluster.
